\documentclass [11pt, a4wide, twoside]{article}

\usepackage{times}
\usepackage{epsfig}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage{fancyhdr}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{verbatim}

% solution switch
\newboolean{showsolution}
\setboolean{showsolution}{true}

\input{../include}

\begin{document}
\section*{Software Modeling and Analysis --- v1.0}

\subsection*{Teaching Assistants}
\begin{itemize}
\item{Pascal Gadient:} \href{mailto:pascal.gadient@inf.unibe.ch}{pascal.gadient@inf.unibe.ch}
\item{Pooja Rani:} \href{mailto:pooja.rani@inf.unibe.ch}{pooja.rani@inf.unibe.ch}
\end{itemize}

\subsection*{Grading}
\begin{itemize}
  \item Scoring scheme: weekly assignments 30\%, final exam 70\%
  \item Each weekly assignment is being graded linearly from 1 to 6 according to the following definition:\\1 - very poor or no solution provided, 2 - poor, 3 - insufficient, 4 - sufficient, 5 - good, 6 - excellent
  \item In order to qualify for the final exam, the average grade of all assignments must be at least 4, \ie sufficient.
\end{itemize}

\subsection*{Organisational Remarks}
\begin{itemize}
\item The lecture slides, examples, and weekly assignments are available at
\begin{quote}
\url{http://scg.unibe.ch/teaching/sma}\\(visit the section ``Resources'' or scroll down to find the weekly assignments)
\end{quote}
\item We will use the Zoom collaboration tool for the practical session after the lecture. We will use the same meeting URL for both the lecture and the practical session (you don't have to reconnect). You can find the relevant Zoom meeting URL on Piazza.
\item Use Piazza only to post questions and to participate in discussions regarding the course. If you have questions related to other affairs, please contact the teaching assistants by email instead.
\end{itemize}

\vspace{4cm}
\begin{center}
\textbf{\textit{\Large{Please continue reading on the next page.}}}
\end{center}

\newpage

\subsection*{Weekly Assignments}
\begin{itemize}
\item We propose for the weekly assignments to work in pairs. However, you can work individually if you prefer to.
\item Answers together with the source code of the exercises (where required) must be \underline{zipped} and sent to \href{mailto:pascal.gadient@inf.unibe.ch}{pascal.gadient@inf.unibe.ch} with the following subject:
\begin{quote}
\textbf{SMA\_Assignment\_ASSIGNMENTNR\_FAMILYNAME1\_FAMILYNAME2}\\example:\hspace{0.5cm}\emph{SMA\_Assignment\_11\_Rani\_Gadient}
\end{quote}
\item Do not copy solutions from others (nor from the Internet). In case of copied solutions, you will collect the grade 1. If you really got stuck, post to Piazza.
\item The course website and the Piazza forum are updated regularly, so please visit them frequently!
\item \textcolor{red}{Your solutions must be received by the teaching assistants \underline{before} the follow-up lecture each Wednesday at 10:15am. Solutions delivered at a later time will get one grade deducted for each 24h period. In case of serious incidents (military service, illness, etc.) you must immediately notify the teaching assistants by email.}
\end{itemize}



\end{document}
