\documentclass [11pt, a4wide, twoside]{article}

\usepackage{times}
\usepackage{epsfig}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage{fancyhdr}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{verbatim}

% solution switch
\newboolean{showsolution}
\setboolean{showsolution}{false} 
%\setboolean{showsolution}{false} 

\input{../include}

\begin{document}

% title
\section*{\ifthenelse{\boolean{showsolution}}{Solution }{}Introduction to Software Modeling and Analysis}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Please hand this exercise in the git repository before 10h15, 27th of September.
Don't forget to register to the \href{https://piazza.com/unibe.ch/fall2016/sma21045}{piazza.com SMA page}

\subsection*{Important remarks}

\begin{itemize}
  \item Scoring scheme: Exercises 30\%,  Exam  70\%
  \item You are expected to create a private git repository on \href{https://bitbucket.org}{https://bitbucket.org} to which the
answers of the exercises and the code have to be committed.
  \item The solutions of the exercises are to be delivered before Tuesday at 10h15. The commit timestamp
will be used to determine if you delivered before the deadline or not. Solutions handed in later will
get one grade subtracted for each 24h period (in case of serious reasons send us an e-mail).
\end{itemize}

\subsection*{How to Qualify for ECTS points}

\begin{itemize}
  \item Each series is rated according to the usual rating system with a scale from 1 to 6, with the following
meaning:
6 - excellent, 5 - good, 4 - sufficient, 3 - not sufficient, 2 - bad, and 1 - no solution provided.
  \item To qualify for the ETCS points, the average mark of all series is required to be a least sufficient
	(i.e. 4). If you are not able to do a series (military service, illness, etc.) let us know as soon as
	possible  
\item Please do not copy solutions from others (nor from the Internet). If you really cannot figure out
something yourself, discuss it with us or post to the mailing list (see below). In case of copied
solutions, you will get a mark of 1.
\end{itemize}

\subsection*{Questions and Discussions:}

\begin{itemize}
  \item For questions and discussions use piazza.com
\end{itemize}

\subsection*{Exercise 1}

Download the book \href{https://ci.inria.fr/pharo-contribution/view/Books/job/UpdatedPharoByExample/lastSuccessfulBuild/artifact/book-result/UpdatedPharoByExample.pdf}{Pharo by Example}

\subsection*{Exercise 2}

Following the instructions in the book install and configure the Pharo environment so as to be able to solve next lecture assignments.

\subsection*{Exercise 3}

\begin{itemize}
\item Explore Pharo a bit. If you want to know more, visit \href{http://files.pharo.org/mooc/}{Pharo MOOC page}.
\end{itemize}

\subsection*{Exercise 4}

\begin{itemize}
  \item Create a private git repository on \href{https://bitbucket.org}{https://bitbucket.org} named sma2016\_exercises\_yourName\_mattriculationNumber
  \item Share it with users scg-nevena and scg-uko
\item Send an e-mail containing your name, matriculation number and the link for cloning the repository
to nevena@inf.unibe.ch and tymchuk@inf.unibe.ch.
\end{itemize}


\end{document}
