\documentclass [11pt, a4wide, twoside]{article}

\usepackage{times}
\usepackage{epsfig}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage{fancyhdr}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{graphicx}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

% solution switch
\newboolean{showsolution}
\setboolean{showsolution}{false} 
%\setboolean{showsolution}{false} 

\input{../include}
\definecolor{mircolor}{rgb}{0.4,0.6,0.2}
\newcommand\ml[1]{\nbc{ML}{#1}{mircolor}}
\usepackage{wasysym}
\newcommand\yesml[1]{\nbc{ML {\textcolor{yellow}\sun}}{#1}{mircolor}}

\begin{document}

% title
\section*{\ifthenelse{\boolean{showsolution}}{Solution }{}Smalltalk: Reflection}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Please submit this exercise to the git repository before 10h15, October 18, 2016.
Don't forget to register on \href{https://piazza.com/unibe.ch/fall2016/sma21045}{piazza.com}.
Also \href{https://www-academia.unine.ch/imoniteur_pbol/PORTAL3S.htm}{register for the course} by Oct 14!

\subsection*{Exercise 1}
Write a method that finds all the abstract methods in the Pharo programming environment.

\subsection*{Exercise 2}
Write a method to find all the methods that override an abstract method in the Pharo system.

\subsection*{Exercise 3}
Write a method that finds the all the classes in Pharo environment with at least one query method.\\ \\
\textbf{Note:} Query methods are those that test a property of an object, \eg having a selector with the prefix ``\ct{is}", ``\ct{was}" or ``\ct{will}".

\subsection*{Exercise 4}
Find all the ``root" methods in the Pharo image. A ``root" method is a method with the selector implemented in a class, such that the superclass of that class does not understand it.

\subsection*{Exercise 4}
Based on the code from the lecture and exercise (\href{http://scg.unibe.ch/download/lectures/sma/Demos/CallGraphDemo/CallGraph-5.st}{CallGraph-5.st}, \href{http://scg.unibe.ch/download/lectures/sma/Demos/CallGraphDemo/Calls.txt}{Calls.txt}), do the following exercise:

By redefining the method \ct{Call>>>#doesNotUnderstand:} dynamically add the instance variable \\ \ct{numberOfArguments} to the class \ct{Call}, and the method
\begin{code}
Call>>#numberOfArguments
	numberOfArguments := args size.
	^ numberOfArguments
\end{code}
 and by executing the code
\begin{code}
(CallGraph fromFile: 'Calls.txt') calls collect: [ :each | each numberOfArguments] 
\end{code}
print the number of arguments for every call in the call graph.


\subsection*{}
Note: For the exercises, {\em file out} the appropriate source code and commit the .st file to the git repository on \href{https://bitbucket.org}{https://bitbucket.org}.
\end{document}
